On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-05 tt_theorem.tex
12/5 morning

            \foreach \theta in {120,-120}{
              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
            }

@@

            \foreach \theta in {180,-120}{
              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
            }

@@

            \foreach \theta in {180,-120,120}{
              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
            }

            \draw[->, blue] (60:1.1)--(60:0.1);
            \draw[->, blue] (0:0.1)--(0:1.1);

@@

    \end{tabular}
    \caption{Direction into a entrance}
    \label{TTT_tunnel_direction}
  \end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tb]
  \centering
    \begin{tabular}{cc}
    \centering
      \begin{minipage}{0.45\linewidth}
      \centering
        \begin{tikzpicture}
	\draw[white] (0:0) -- (120:1);
	\draw[white] (0:0) -- (-60:1);
	\draw[white] (0:0) -- (0:1);

            \foreach \theta in {0}{
              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
            }
            \draw (-60:1) circle [radius=0.05];
            \draw (60:1) circle [radius=0.05];

          \node at (0,-2) {Point $n_1$ and $n_2$ are free};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.45\linewidth}
      \centering
        \begin{tikzpicture}
	\draw[white] (0:0) -- (0:1);
	\draw[white] (0:0) -- (120:1);
	\draw[white] (0:0) -- (-90:2);

            \foreach \theta in {0}{
              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
            }
            \draw (-60:1) circle [radius=0.05];

          \node at (0,-2) {Point $n_1$ is occupied};
        \end{tikzpicture}
      \end{minipage}
    \end{tabular}
    \caption{Exit of Tunnel}
    \label{TTT_tunnel_exit}
\end{figure}

@@

%If $i - h > 1$ and $j$ is such that $h \leq j<i$, then $\#bc(C_{j-1}) \geq \#bc(C_{j})$ because all neighbors of $w[j]$ are occupied by beads forming the tunnel so that any $w[i+1..]$ cannot reach neighbors of $w[j]$. 
%Thus, inside this tunnel, binding capabilities never increased.

@@

@@

\begin{figure}
  \begin{center}
        \begin{tikzpicture}
        \draw[->,white] (-70:0.1) -- (-70:3);
          \foreach \theta in {60,-60,120,0}{
            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
          }

@@

          \begin{scope}[shift=(-120:1)]
            \fill[blue](0,0) circle [radius=0.05];
            \foreach \theta in {-120,-60,180}{
              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
            }

          \end{scope}
        \end{tikzpicture}
    \caption{Case of $S[h-1..h+1] = bbt$}
    \label{TTT_tunnelC_enter_usingBond}
  \end{center}
\end{figure}

\begin{proof}
%	The bead $w[i+1]$ consumes one hand and provide nothing, that is, $\#bc(C_{i}) \geq \#bc(C_{i+1})$.
%	The bead $w[i]$ consumes bond because $S[i] = b$.
%	See Fig.~\ref{TTT_tunnelC_enter_usingBond}.
%	The bead $w[i+2]$ is stabilized at a point of neighbors of $w[i]$.
%	If $w[i]$ consumes just one hand, $w[i]$ leaves a hand, that is, $\#bc(C_{i-1}) \geq \#bc(C_{i})$.
%	Then, $w[i+2]$ consumes $w[i]$'s hand.
%	Thus, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
%	On the other hand, if $w[i]$ forms two bonds, then even if $w[i+2]$ provides two free hands, $\#bc(C_{i-1}) - \#bc(C_{i}) = \#bc(C_{i+1}) - \#bc(C_{i+2})$.
%	Thus, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
%	This argument actually work also for the case when $w[i]$ is stabilized rather by binding.

%\begin{lemma}
%\label{TTT_tunnelC_lemma}
%Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$, arity $\alpha = 2$. We assume $S[h..i+1] = bt^{(i-h)}b \quad (1<h<i)$. If at least one of $w[h+1..i]$ is stabilized by tunnel $C$, then $\#bc(C_{h-3}) > \#bc(C_{h+1})$ and $\#bc(C_{h-3}) > \#bc(C_i)$.
%\end{lemma}

%\begin{proof}[Lemma~ \ref{TTT_tunnelC_lemma}]
%Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha = 2$.
%Assume $S[h..i+1] = bt^{i-h}b (h<i)$. If at least one of $w[h+1..i]$ are stabilized by tunnel $C$, then only $w[h+1]$ can use tunnel $C$ because if $w[g]$ which is one of $w[h+2..i]$, with $h+2 \leq g \leq i$ is stabilized by tunnel $C$, $C_g$ is a terminal.
%
%
%Let us consider stabilization $S[h-1..h+1] = tbt$ or $S[h-1..h+1] = bbt$ as follows. In result, $\#bc(C_{h-3}) > \#bc(C_{h+1})$. In addition according to Lemma~\ref{TTT_exit} $\#bc(C_{h+1}) \geq \#bc(C_{i})$. Thus, $\#bc(C_{h-3}) > \#bc(C_{h+1})$ and $\#bc(C_{h-3}) > \#bc(C_{i})$.
%\\
%
%\subsubsection{Case of $S[h-1..h+1] = bbt$}
%See Fig.~\ref{TTT_tunnelC_enter_usingBond}.
%If $w[h-1]$ forms one bond, then it leaves one free bond, but it is consumed by $w[h+1]$.
%In addition, $w[h]$ has to bound.
%Thus, in this cases, binding capability decreases by 1.
%If $w[h-1]$ forms two bonds, then it does not leave any bond.
%In addition, $w[h]$ has to be bound.
%Thus, in this case, even if $w[h+1]$ supplies two free bonds, binding capability decreases by 1.

%\subsubsection{Case of $S[h-1..h+1] = tbt_a$}
%Fig.\ref{TTT_tunnelC_enter_usingTunnel} exhibits all the two kinds of stabilization depending on structures of tunnel C.
%
%%\item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
%  In this figure, Bead $n_4$ has at least one binding so that $w[h-1]$ has to bound $n_4$. Moreover, $w[h]$ has to bind to one of $n_1, n_2, n_3$ in order to stabilize deterministically. On the other hand, $w[h+1]$ can supply two bindings but has only two free neighbors. One of them is occupied by a successor. Therefore $w[h+1]$ can only bind one of $n_5, n_6$, that is, $w[h+1]$ supplies at most one binding. Thus, this case $\#bc(C_{h-1}) > \#bc(C_{h+1})$.
%
%  These cases are divided on number of capabilities that $w[h-1]$ consumes.
%  \begin{itemize}
%  \item[-]{$w[h-1]$ does not consume any bindings}\\
%  According to Lemma~\ref{TTT_exit}, $\#bc(C_{h-3}) \geq \#bc(C_{h-1})$ because of $S[h-1] = t$.
%    $w[h]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically so that  $\#bc(C_{h-1}) > \#bc(C_{h})$.
%    $w[h+1]$ has to be bound to $w[h-1]$ because $w[h-1]$ has bindings, that is, $w[h+1]$ consumes at least one hand and supplies at most one hand so that $\#bc(C_{h}) \geq \#bc(C_{h+1})$. Thus, in this cases $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
%%     This time, let us consider either $n_4$ is occupied or not. If $n_4$ is occupied, then $w[h-1]$ has no active bindings that is this situation consumes some binding capabilities. If $n_4$ is free and $w[h+2]$ is stabilized in $n_4$, then $w[h-1]$ has to bind $w[h+2]$. Therefore, In this case, stabilization of $w[h-1..h+2]$ consumes some bindings. If $n_4$ is free and $w[h+2]$ is stabilized except $n_4$, then this oritatami system has to use two binding capabilities in order to bind $w[h+2]$. Therefore, in this case consumes some bindings. Thus in this cases $\#bc(C_{h-1}) > \#bc(C_{h+2})$.
%
%  \item[-]{$w[h-1]$ consumes one binding}\\
%    In this case, $w_{h}$ has to be bound one of $n_1, n_2, n_3$. In addition, $w[h-1]$ and $w[h+1]$ are not supply any bindings. Thus, in this cases consume some binding capabilities.
%  \item[-]{$w[h-1]$ consumes two bindings}\\
%    In this case, $w[h-1]$ already consumes two binding. $w[h]$ has to be bound. $w[h+1]$ supplies two bindings. Thus, in this cases $\#bc(C_{h-1}) > \#bc(C_{h+1})$.
%   
%  \end{itemize}

%\begin{figure}
%  \centering
%    \begin{tabular}{cc}
%      
%      \begin{minipage}{0.48\hsize}
%      \centering
%        \begin{tikzpicture}
%
%          \fill[transform canvas={shift=(0:0)}](0,0) circle [radius=0.1];
%          
%          \foreach \theta in {60,-60,120,-120,180}{
%            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
%          }
%
%          \fill[blue](0:1) circle [radius=0.05];
%          \draw[->, blue] (0:0.1)--(0:0.9);
%
%          \node[below] at (-60:1) {$n_4$};
%
%          \begin{scope}[shift=(0:2)]
%            \fill[blue](0,0) circle [radius=0.05];
%
%            
%            \foreach \theta in {120,60,-60,0}{
%             \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
%            }
%
%            \draw[->, blue] (180:0.9)--(180:0.1);
%            \draw[->, blue] (-120:0.1)--(-120:0.9);
%
%            \node[below] at (180:1) {$w_{[h-1]}$};
%            \node[above] at (0:0) {$w_{[h]}$};
%            \node[below] at (-120:1) {$w_{[h+1]}$};
%
%            \node[above] at (120:1) {$n_3$};
%            \node[above] at (60:1) {$n_2$};
%            \node[right] at (0:1) {$n_1$};
%
%            \begin{scope}[shift=(-120:1)]
%              \fill[blue](0,0) circle [radius=0.05];
%              \foreach \theta in {-120,-60}{
%                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
%              }
%
%              \node[right] at (-120:1) {$n_5$};
%              \node[right] at (-60:1) {$n_6$};
%            \end{scope}
%            
%          \end{scope}
%
%          \node at (1.2,-2.5) {Pattern 1};
%        \end{tikzpicture}
%      \end{minipage}
%
%      \begin{minipage}{0.48\hsize}
%      \centering
%        \begin{tikzpicture}
%
%          \fill(0,0) circle [radius=0.1];
%          
%          \foreach \theta in {60,0,120,-120,180}{
%            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
%          }
%
%          \draw[->, blue] (-60:0.1)--(-60:0.9);
%
%
%          \begin{scope}[shift=(-60:1),shift=(0:1)]
%            \fill[blue](0,0) circle [radius=0.05];
%            \fill[blue](180:1) circle [radius=0.05];
%
%            
%            \foreach \theta in {120,60,0,-60}{
%              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
%            }
%
%            \draw[->, blue] (180:0.9)--(180:0.1);
%            \draw[->, blue] (-120:0.1)--(-120:0.9);
%
%            \node[below] at (180:1) {$w_{[h-1]}$};
%            \node[above] at (0:0) {$w_{[h]}$};
%            \node[below] at (-120:1) {$w_{[h+1]}$};
%
%            \node[above right] at (120:1) {$n_3$};
%            \node[right] at (60:1) {$n_2$};
%            \node[right] at (0:1) {$n_1$};
%
%            \begin{scope}[shift=(-120:1)]
%              \fill(0,0) circle [radius=0.05];
%              \foreach \theta in {180,-120,-60}{
%                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
%              }
%
%              \node[left] at (180:1) {$n_4$};
%              \node[right] at (-120:1) {$n_5$};
%              \node[right] at (-60:1) {$n_6$};
%            \end{scope}
%            
%          \end{scope}
%
%          \node at (1.25,-4) {Pattern 2};
%        \end{tikzpicture}
%      \end{minipage}
%
%      
%      
%    \end{tabular}
%    \caption{Case of $S[h-1..h+1] = tbt$}
%    \label{TTT_tunnelC_enter_usingTunnel}
%\end{figure}

%\end{proof}

@@

%\begin{figure}[tb]
% \centering
%    \begin{tikzpicture}
%	\fill[shift=(180:1)] (0,0) circle [radius=0.1];
%      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
%      
%      \draw[->] (180:0.9) -- (180:0.1);
%
%	\node[above] at (180:1) {$w_{[i-2]}$};
%	\node[below] at (180:0) {$w_{[i-1]}$};
%	\node[above] at (0:1) {$n_0$};
%
%	\foreach \theta in {0,60,-60,120,-120}{
%   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
%  	}
% 	\node[above] at (60:1) {$n_1$};
%	\node[below] at (-60:1) {$n_2$};
%	\node[above] at (120:1) {$n_3$};
%	\node[below] at (-120:1) {$n_4$};
%    \end{tikzpicture}
%    \caption{$\alpha = 4$: when $w[i]$ is stabilized}
%    \label{TTT_a4_lemma_fig}
%\end{figure}

%\begin{lemma}
%\label{TTT_a4_2b_lemma}
%Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 4$.
%When a bead is stabilized by bond, it forms at least two bonds.
%\end{lemma}
%
%\begin{proof}%[proof of lemma]
%Suppose $w[i]$ were stabilized by only one bond. See Fig.~\ref{TTT_a4_lemma_fig}. If $n_3$ is free, $w[i-2]$ still has some bonds because of arity $\alpha = 4$. Thus, $n_4$ must be occupied; otherwise, $w[i]$ would be stabilized nondeterministically at $n_3$ and $n_4$. Moreover, also $n_2$ has to be occupied for deterministic and also $n_0, n_1$. $n_1$ has some hands because $n_3$ is free. Therefore, $w[i]$ is stabilized at $n_3$ and it has to use at least two hands. It contradict assumption.
%\end{proof}

@@

	\node at (0:2.5) {$n$};
	\node[shift=(60:1)] at (0:2) {$n+1$};
    \end{tikzpicture}
    \caption{the first bead out of $\hexagon_{w[-n+1]}^n$}
    \label{TTT_a4_first}
\end{figure}

%\begin{lemma}
%\label{TTT_a3_2b_lemma}
%Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. 
%If $S[i] = t$ or $t^\times$ and $S[i+1] \neq \blacksquare$, then the bead $w[i]$ consumes also at least one bond. 
%% Let $p$ be a point whose neighbors is occupied at least two point. If $w[i]$ is not stabilized and $w[i-1]$ includes neighbors of $p$, then $w[i]$ is stabilized at $p$ with at least one bond, $w[i]$ is stabilized at another point of $p$ otherwise with at least two bond except any neighbors of $p$ is occupied.
%\end{lemma}
%
%\begin{proof}%[proof of lemma]
%Both $n_3$ and $n_4$ are occupied because $S[i] = t$ or $t^\times$.
%Suppose $w[i]$ were stabilized without any bond.
%Then, all neighbors of $n_3$ must be occupied as long as the bead at $n_3$ is not singular; otherwise, a bead at $n_3$ would be capable of forming a bond with $w[i]$.
%That is, $n_1$ is occupied.
%We can continue this argument in clockwise manner to fill the neighbors of $w[i]$ until a singular bead is encountered, if any.
%If needed, the same argument is applied starting from $n_4$ in counter-clockwise manner.
%Thus, all neighbors of $w[i]$ must be occupied but then $S[i+1] = \blacksquare$, contradiction. \qed
%\end{proof}

@@

	\foreach \theta in {60,-60,120,-120}{
   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
  	}
	 \draw [shift=(60:1)] (0.95,-0.05) rectangle (1.05,0.05);
	  \draw [shift=(180:1),shift=(120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
 	\node[above] at (60:1) {$n_1$};
	\node[below] at (-60:1) {$n_2$};
	\node[above] at (120:1) {$n_3$};
	\node[below] at (-120:1) {$n_4$};
	\node[above, shift=(0:1)] at (60:1) {$n_{-1}$};
	\node[above, shift=(180:1)] at (120:1) {$n_5$};
    \end{tikzpicture}
    \end{minipage}

@@

	\foreach \theta in {0,-60,120,-120}{
   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
  	}
	\draw [shift=(60:1)] (0.95,-0.05) rectangle (1.05,0.05);
	\draw [shift=(60:1), shift=(60:1)] (-0.05,-0.05) rectangle (0.05,0.05);
	\draw [shift=(60:1), shift=(120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
	  \draw [shift=(180:1),shift=(-120:1)] (-0.05,-0.05) rectangle (0.05,0.05);

@@

	\foreach \theta in {0,60,-60,-120}{
   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
  	}
	\draw [shift=(120:1), shift=(60:1)] (-0.05,-0.05) rectangle (0.05,0.05);
	\draw [shift=(120:1), shift=(120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
	\draw [shift=(120:1), shift=(180:1)] (-0.05,-0.05) rectangle (0.05,0.05);

@@

\begin{theorem}[$\delta = 1, \alpha = 3$]
Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite conformations of length is $2n + 14$.
\end{theorem}

%We consider cases which $w[i-1]$ is two distances away from the singular point.
%Let us show that $\#bc(C_{i-1}) > \#bc(C_i)$, that is, when $w[i]$ is stabilized, $w[i]$ uses at least two hands.
%Fig.\ref{TTT_a3_w} exhibits all the three kinds of possibility of stabilized $w[i]$.
%Suppose $w[i]$ were able to be stabilized with using one hand in each cases.
%
%% Then, $w[i]$ can be also stabilized at $n_3$. 
%
%\begin{paragraph}{Case of straight}
%\begin{itemize}
%\item[-] Case of $n_3$ is free\\
%The bead $w[i-2]$ must not have bonds because $w[i]$ is stabilized deterministically so that five neighbors of $w[i-2]$ must be occupied.
%Therefore $n_5$ must be occupied.
%We can continue this argument in clockwise manner to fill the neighbors of $n_3$ until $n_1$.
%However, two neighbors of $n_1$ must be free because they are $n_3$ and the point of $w[i]$, contradict.
%
%\item[-] Otherwise\\
%Both $n_3$ and $n_4$ are occupied.
%One of $n_1$ and $n_2$ must be free because $S[i] = b$.
%We assume $n_1$ is free, then all neighbors of $n_1$ must be occupied because $n_3$ is occupied.
%However, one of neighbors $n_1$ is a point which $w[i]$ is stabilized, contradict.
%\end{itemize}
%
%Therefore, this case contradict assumption.
%\end{paragraph}
%
%\begin{paragraph}{Case of obtuse}
%\begin{itemize}
%\item[-] Case of $n_3$ is free\\
%Any neighbors of $n_3$ have to be occupied but the point which $w[i]$ is stabilized is free. Thus $n_3$ has to be occupied.
%\item[-] Case of $n_4$ is free\\
%The point $n_2$ must be occupied because $n_4$ is free and $n_5$ must be occupied.
%Therefore $n_0$ is occupied.
%The bead $w[i]$ forms just one bond so that one of $n_0, n_3$ leave some hands or both of them do not leave any bonds.\\
%If $n_0$ has some hands, then $n_3$ does not have any hands so that $n_{-3}$ is occupied. 
%We can continue this argument in clockwise manner to fill the neighbors of $w[i]$.
%That is, $S[i] = \blacksquare$, contradict.
%
%If $n_3$ has some hands, then $n_0$ does not have any hands so that neighbors of $w[i]$ are occupied. In the same previous way, contradict.\\
%If both of $n_0, n_3$ do not have any hands, then both of $n_{-1}, n_{-3}$ are occupied. If one of $n_{-1}, n_{-3}$ has some hands, the other does not have any hands so that $n_{-2}$ is occupied. If both of $n_{-1}, n_{-3}$ do not have any hands, $n_{-2}$ has to be occupied and $n_{-2}$ has some hands, contradict.
%\item[-] Case of $n_2$ is free\\
%Any neighbors of $n_2$ have to be occupied so that $n_0$ is occupied. Any neighbors of $n_0$ except $n_2$ have to be also occupied but the point which is stabilized $w[i]$ is free. Thus $n_2$ has to be occupied.
%\item[-] Case of $n_0$ is free\\
%Any neighbors of $n_0$ have to be occupied so that $n_{-1}$ is occupied. Any neighbors of $n_{-1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free. Thus $n_0$ has to be occupied. 
%\end{itemize}
%\end{paragraph}
%
%
%
%\begin{paragraph}{Case of acute}
%\begin{itemize}
%\item[-] Case of $n_4$ is free\\
%The point $n_4$ and a point which is stabilized $w[i]$ are free so that  $w[i-2]$ has some bonds.
%However, $w[i]$ can be also stabilized $n_4$ in this case. Thus, $n_4$ has to be occupied.
%\item[-] Case of $n_2$ is free\\
%The point $n_0$ has to be occupied. The point $n_1$ has to be also occupied because five neighbors of $n_0$ must be occupied.
%We consider this case just like case of obtuse and that $n_4$ is free. Then if $w[i-2]$ binds $w[i]$, any $n_{-1}, n_{-2}, n_{-3}$ are occupied. If $n_1$ binds $w[i]$, this case is same. Also if $n_1$ and $w[i-2]$ do not have any hand, any $n_{-1}, n_{-2}, n_{-3}$ are occupied. Therefore, $w[i+1]$ cannot be provided.
%\item[-] Case of $n_0$ is free\\
%Any neighbors of $n_0$ have to be occupied so that $n_{1}$ is occupied. Any neighbors of $n_{1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free. Thus $n_0$ has to be occupied. 
%\item[-] Case of $n_1$ is free\\
%Any neighbors of $n_1$ have to be occupied so that $n_{-1}$ is occupied. Any neighbors of $n_{-1}$ except $n_1$ have to be also occupied but the point which is stabilized $w[i]$ is free. Thus $n_1$ has to be occupied. 
%\end{itemize}
%
%Therefore, any situations contradict $S[i] = b$.
%\end{paragraph}\\
%
%
%Hence, $w[i]$ uses at least two bonds if $w[i-1]$ is at least two distances away the singular point.
%The size of $ \hexagon^2_0 = 19$ and this number contain the singular point, its successor and its three neighbors which is it binds to. Therefore 14 times  $w[i]$ can be stabilized by forming one bond.
%Therefore, a deterministic unary oritatami system at $\delta = 1$ and $\alpha = 3$ can yield only finite conformation of length is $2n + 14$.

\begin{figure}
  \begin{center}
  \begin{tabular}{c c}
  \begin{minipage}{0.48\hsize}
  \centering
    \begin{tikzpicture}
      	\fill (0,0) circle [radius=0.1];
        \fill[blue] (60:1) circle [radius=0.05];
         \fill[blue] (120:1) circle [radius=0.05];
        \fill (0:1) circle [radius=0.1];

@@

	\node[below] at (0:0) {$w[i-1]$};
	\node[above] at (60:1) {$w[i]$};
	\node[above, shift=(0:1)] at (60:1) {$w[i+1]$};
	\end{tikzpicture}
    \end{minipage}
    \end{tabular}
    \caption{The bead $w[i]$  the first bead outside $\hexagon^n_0$: $w[i+1]$ elongated to west (left), $w[i+1]$ elongated to east (right)}
    \label{fig:ttt_d2}
  \end{center}
\end{figure}

%By Tunnel Troll Theorem, any tunnel sections which represented in $bbt^+$ or $bt^+bt^+$ consume binding capabilities. If the sequence $S$ is free from any subsequence of the form $bt^+bt^+$, then it can factorize as $S = u_1 u_2 u_3 \cdots$ for some $u_1 , u_2 , u_3 , \cdots \in \{b\} \cup bbt^+$. Assume the length of $\sigma$ is $n$, seed supplies at most $2n$ binding capabilities. Therefore formula \ref{TTT_only_bond} hold.
%
%\begin{eqnarray}
%  \exists i \in \mathbb{N} \quad s.t. \quad u_{i-1} , u_i , u_{i+1} , u_{i+2} , \cdots \in \{ b \}
%  \label{TTT_only_bond}
%\end{eqnarray}
%
%
%Let us represent $S$ as $S[i.i+1...] = v_i v_{i+1} v_{i+2} \cdots$ for some $v_i, v_{i+1}, v_{i+2}, \cdots \in \{ a, o\}$ where if $v_k$ is $a$, then $v_{k+1}$ is bound to $v_{k-1}$, if $v_k$ is $o$, then $v_{k+1}$ is NOT bound to $v_{k-1}$.
%
%
%Let us consider the case of $v_k$ is $o$. See Fig.\ref{TTT_case_of_o}. $w[i-1]$ consumes some binding capabilities because $v_{i-1}$ is $b$. If the number of $w[i-1]$'s bindings is one binding, then $w[i+1]$ has to be bound except $n_1$ or $n_2$ so that $w[i+1]$ must consumes two bindings except the case of $n_1$ and $n_2$ are occupied and $w[i]$ consumes at least one binding. If $n_1$ and $n_2$ are occupied, then $w[i-1]$'s bindings are inactive, that is, $w[i-1]$ consumes two binding capabilities. Therefore, this case consumes binding capabilities. If $w[i-1]$ dose Not have any bindings, then $w[i-1]$ already consumes two bindings. In addition, $w[i]$ and $w[i+1]$ consume at least one binding. Therefore this case consumes binding capabilities. Thus, the formula \ref{TTT_only_a} hold and according to the formula \ref{TTT_only_bond} and the formula \ref{TTT_only_a}, the formula \ref{TTT_structure} is hold. Thus, in this case, oritatami system can yield infinite structures but they are only zig-zag conformation.

%
%
%\begin{eqnarray}
%  \exists j \in \mathbb{N} \quad s.t. \quad u_j , u_{j+1} , u_{j+2} , \cdots \in \{ a \}
%  \label{TTT_only_a}
%\end{eqnarray}
%
%\begin{eqnarray}
%  | S | > \forall m \in \mathbb{N} \quad \to \quad \exists n \in \mathbb{N} \quad s.t. \quad S[n], S[n+1], \cdots \in \{ a \}
%  \label{TTT_structure}
%\end{eqnarray}
%
%\begin{figure}
%  \begin{center}
%    \begin{tikzpicture}
%      
%      \fill[transform canvas={shift=(-120:1)}](0,0) circle [radius=0.1];
%      
%      \fill[blue](0:0) circle [radius=0.05];
%      \fill[blue](0:1) circle [radius=0.05];
%      \fill[shift=(0:1), blue](40:1) circle [radius=0.05];
%
%      \draw[->, blue] (-120:1) edge[bend left] (-120:0.1);
%      \draw[->, blue] (0:0.1) -- (0:0.9);
%      \draw[->,transform canvas={shift=(0:1.2)}, blue] (50:0) -- (47:0.8);
%      
%      \draw[shift=(60:1)](-0.05,-0.05) rectangle (0.05,0.05);
%      \draw[shift=(-60:1)](-0.05,-0.05) rectangle (0.05,0.05);
%      
%      \node[below] at (-120:1) {$w[i-2]$};
%      \node[above] at (0:0) {$w[i-1]$};
%      \node[below] at (0:1) {$w[i]$};
%      \node[right, shift=(0:1)] at (40:1) {$w[i+1]$};
%
%      \node[above] at (60:1) {$n_1$};
%      \node[below] at (-60:1) {$n_2$};
%        
%    \end{tikzpicture}
%    \caption{Case of $S[i]$}
%    \label{TTT_case_of_o}
%  \end{center}
%\end{figure}
%

>>>>

            \foreach \theta in {120,-120}{
              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
            }

@@

            \foreach \theta in {180,-120}{
              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
            }

@@

            \foreach \theta in {180,-120,120}{
              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
            }

            \draw[->, blue] (60:0.9)--(60:0.1);
            \draw[->, blue] (0:0.1)--(0:1.1);

@@

    \end{tabular}
    \caption{Direction into an entrance of a tunnel: (Left) straight, (Middle) obtuse, (Right) acute. The bead $w[i]$ is stabilized at an entrance and $w[i+1]$ is stabilized inside a tunnel.}
    \label{TTT_tunnel_direction}
  \end{center}
\end{figure}

@@

@@

\begin{figure}[tb]
  \centering
    \begin{tabular}{cc}
    \centering
      \begin{minipage}{0.45\linewidth}
      \centering
        \begin{tikzpicture}
	\draw[white] (0:0) -- (120:1);
	\draw[white] (0:0) -- (-60:1);
	\draw[white] (0:0) -- (0:1);

            \foreach \theta in {0}{
              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];            }
            \draw (-60:1) circle [radius=0.05];
            \draw (60:1) circle [radius=0.05];

        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.45\linewidth}
      \centering
        \begin{tikzpicture}

	\draw[white] (0:0) -- (120:1);
	\draw[white] (0:0) -- (-60:1);
	\draw[white] (0:0) -- (0:1);

            \foreach \theta in {0}{
              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
            }
            \draw (-60:1) circle [radius=0.05];

        \end{tikzpicture}
      \end{minipage}
    \end{tabular}
    \caption{Two kinds of exit of a tunnel: (Left) Both $n_1$ and $ n_2$ are free, (Right) One of $n_1$ and $n_2$ is occupied.}
    \label{TTT_tunnel_exit}
\end{figure}

@@

\begin{proof}

\begin{figure}[tb]
  \begin{center}
        \begin{tikzpicture}
        \draw[->,white] (-70:0.1) -- (-70:3);
          \foreach \theta in {60,-60,120,0}{
            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
          }

@@

          \begin{scope}[shift=(-120:1)]
            \fill[blue](0,0) circle [radius=0.05];
            \foreach \theta in {-120,-60,180}{
              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
            }

          \end{scope}
        \end{tikzpicture}
    \caption{Case of $S[i+2] = t_a$.}
    \label{TTT_tunnelC_enter_usingBond}
  \end{center}
\end{figure}

@@

@@

	\node at (0:2.5) {$n$};
	\node[shift=(60:1)] at (0:2) {$n+1$};
    \end{tikzpicture}
    \caption{The first bead out of $\hexagon_{w[-n+1]}^n$}
    \label{TTT_a4_first}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{theorem}[$\delta = 1, \alpha = 3$]
Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite conformations of length is $4n + 14$.
\end{theorem}

@@

	\foreach \theta in {60,-60,120,-120}{
   	   \draw [shift=(\theta:1)] (0:0) circle [radius=0.05];
  	}
	 \draw [shift=(60:1), ] (0:1) circle [radius=0.05];
	  \draw [shift=(180:1),shift=(120:1)] (0:0) circle [radius=0.05];
 	\node[above] at (60:1) {$n_1$};
	\node[below] at (-60:1) {$n_2$};
	\node[above] at (120:1) {$n_3$};
	\node[below] at (-120:1) {$n_4$};
	\node[above, shift=(0:1)] at (60:1) {$n_{-1}$};
	\node[above, shift=(180:1)] at (120:1) {$n_5$};
    \end{tikzpicture}
    \end{minipage}

@@

	\foreach \theta in {0,-60,120,-120}{
   	   \draw [shift=(\theta:1)](0:0) circle [radius=0.05];
  	}
	\draw [shift=(60:1)] (0:1) circle [radius=0.05];
	\draw [shift=(60:1), shift=(60:1)] (0:0) circle [radius=0.05];
	\draw [shift=(60:1), shift=(120:1)] (0:0) circle [radius=0.05];
	  \draw [shift=(180:1),shift=(-120:1)] (0:0) circle [radius=0.05];

@@

	\foreach \theta in {0,60,-60,-120}{
   	   \draw [shift=(\theta:1)] (0:0) circle [radius=0.05];
  	}
	\draw [shift=(120:1), shift=(60:1)] (0:0) circle [radius=0.05];
	\draw [shift=(120:1), shift=(120:1)] (0:0) circle [radius=0.05];
	\draw [shift=(120:1), shift=(180:1)] (0:0) circle [radius=0.05];

@@

\begin{figure}[tb]
  \begin{center}
  \begin{tabular}{c c}
  \begin{minipage}{0.48\hsize}
  \centering
    \begin{tikzpicture}
      	\fill (0,0) circle [radius=0.1];
        \fill[blue] (60:1) circle [radius=0.05];
         \fill[blue] (120:1) circle [radius=0.05];
        \fill (0:1) circle [radius=0.1];

@@

	\node[below] at (0:0) {$w[i-1]$};
	\node[above] at (60:1) {$w[i]$};
	\node[above, shift=(0:1)] at (60:1) {$w[i+1]$};
	\end{tikzpicture}
    \end{minipage}
    \end{tabular}
    \caption{The bead $w[i]$  the first bead outside $\hexagon^n_0$: (Left) $w[i+1]$ elongated to west, (Right) $w[i+1]$ elongated to east.}
    \label{fig:ttt_d2}
  \end{center}
\end{figure}
